---
title: "Q2_SSAHA"
author: "Subhashree Saha"
date: "2022-11-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
MLE=function(n1){
  #1)function to compute mle
  MyMLE=function(data1){
    fit = optimize(data1,c(0,50),maximum = T)
    
    return(log(fit$maximum))}
  

  
  loglikegamma=function(shape){
    #2i)simulating from gamma distribution
    data2=rgamma(n=n1, shape=1.5, scale = 2.2) 
    
    l=sum(dgamma(data2,shape,scale=2.2,log=T))
    return(l)
  }
  
  v<-c((MyMLE(loglikegamma)))
  #2ii and iii)
  for(x in 1:1000){
    v<-append(v,(MyMLE(loglikegamma)))
    
  }
return(v) 
}
```
Histogram of estimated MLE when n=20\
```{r}
  #2iv)
  hist(MLE(20), col="lightblue",xlab='estimated MLE of log alpha',main=' Histogram of the estimated MLEs of log alpha when n=20')
  #2v)
  abline(v=log(1.5), col="red", lwd=3, lty=2)
```
2.5 percentile point when n=20\
```{r}
#2vi)
q11=quantile(MLE(20),probs=0.025)
q11
```
97.5 percentile point when n=20\
```{r}
q12=quantile(MLE(20),probs=0.975)
q12
```

Histogram of estimated MLE when n=40\
```{r}
  #3)
  hist(MLE(40), col="lightblue",xlab='estimated MLE of log alpha',main=' Histogram of the estimated MLEs of log alpha when n=40')
  
  abline(v=log(1.5), col="red", lwd=3, lty=2)
```
2.5 percentile point when n=40\
```{r}

q21=quantile(MLE(40),probs=0.025)
q21
```
97.5 percentile point when n=40\
```{r}
q22=quantile(MLE(40),probs=0.975)
q22
```

Histogram of estimated MLE when n=100\
```{r}
  #4)
  hist(MLE(100), col="lightblue",xlab='estimated MLE of log alpha',main=' Histogram of the estimated MLEs of log alpha when n=100')
  
  abline(v=log(1.5), col="red", lwd=3, lty=2)
```
2.5 percentile point when n=100\
```{r}

q31=quantile(MLE(100),probs=0.025)
q31
```
97.5 percentile point when n=100\
```{r}
q32=quantile(MLE(100),probs=0.975)
q32
```
5)Gap between 2.5 and 97.5-percentile points

when n is 20
```{r}
gap1=q12-q11
gap1
```
when n is 40
```{r}
gap2=q22-q21
gap2
```
when n is 100
```{r}
gap3=q32-q31
gap3
```
SO, we see that the gap between 2.5 and 97.5-percentile points are shrinking as sample size n is increasing.





